---
title: "Gothic Textual Data"
author: "Margaret Butler"
date: "12/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gutenbergr)
library(tidyverse)
library(stringr)
library(fs)
library(scales)
library(lubridate)
library(dplyr)
library(knitr)
library(tibble)
library(foreign)
library(readr)
library(janitor)
library(tibble)
library(purrr)
library(ggplot2)
library(ggrepel)
library(tidytext)
library(tokenizers)
library(textdata)
library(wordcloud)


## load packages

```
## Looking at Gothic Literature

Downloading books I want to look at from the gutenbergr package. Books I am looking at in this are *Frankenstein*, *The Strange Case of Dr. Jekyll and Mr. Hyde*, *Carmilla*, *The Phantom of the Opera*, and *Dracula*.

## Gutenberg Book ID Numbers

1. Frankenstein 84
2. The Strange Case of Dr. Jekyll and Mr. Hyde 43
3. Carmilla 10007
4. The Phantom of the Opera 175
5. Dracula 345

```{r, inclue=FALSE, message=FALSE}

gothic <- gutenberg_download(c(84, 43, 10007, 175, 345), meta_fields = "title")

gothic$row_num <- seq.int(nrow(gothic))


frankenstein <- gutenberg_download(84)
jekyllhyde <- gutenberg_download(43)
carmilla <- gutenberg_download(10007)
phantom <- gutenberg_download(175)
dracula <- gutenberg_download(345)

## downloading the books into one big data set and then into separate data sets
## I discovered later that I did'nt need to download the texts separately but I'm leaving them in here for now

tidy_gothic <- gothic %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

messy_gothic <- gothic %>% 
  unnest_tokens(word, text)

## need a messy_gothic and a separate tidy_gothic because one includes the pronouns I want to count while the other removes pronouns. I'm looking at both.

tidy_frankenstein <- frankenstein %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_jekyllhyde <- jekyllhyde %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_carmilla <- carmilla %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_phantom <- phantom %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_dracula <- dracula %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

## tidying words so I can pick through them at my leisure
## I am a goofball and realized that the reason I cannot analyze the pronoun usage is because stop_words removes pronouns...

```

```{r sentiment over course of novels}

sentiment_time <- tidy_gothic %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(title, index = row_num %/% 80, sentiment) %>% 
  spread(sentiment, n, fill = 0) %>% 
  mutate(sentiment = positive - negative)

sentiment_dist <- ggplot(sentiment_time, aes(index, sentiment, fill = title)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~title, ncol = 2, scales = "free_x")

write_rds(sentiment_time, "gothiclit/sentiment_time.rds")

```

These graphs display the change in positive versus negative sentiment of the words as each text progresses

I want to map pronoun usage and negative sentiment across the books to see if I can track monstrosity, but I genuinely have no idea how to do all of that. So, I am frustrated.


```{r}

tidy_gothic %>% 
  count(word, sort = TRUE) 
  
## checking the most common words across all five texts

```

Looking for words we associate with monstrosity.



```{r }

```

*The Phantom of the Opera* skews the data because Christine and Raoul are in the top ten most frequent words! Moving on to look at each book individually.

```{r}

tidy_frank <- tidy_frankenstein %>% 
   count(word, sort = TRUE)

## words that are unique to Frankenstein due to status as names: elizabeth

tidy_jek <- tidy_jekyllhyde %>% 
  count(word, sort = TRUE)

## words that are unique to Jekyll and Hyde due to status as names: poole, utterson, jekyll, hyde

tidy_carm <- tidy_carmilla %>% 
  count(word, sort = TRUE)

## words that are unique to Carmilla due to status as names: carmilla

tidy_drac <- tidy_dracula %>% 
  count(word, sort = TRUE)

## words that are unique to Dracula due to status as names: van, helsing, lucy, mina, jonathan

tidy_phan <- tidy_phantom %>% 
  count(word, sort = TRUE)

## words that are unique to Phantom due to status as names: christine, raoul, erik, richard

```

```{r}
no_names <- messy_gothic %>% 
  filter(word != "elizabeth") %>% 
  filter(word != "poole") %>% 
  filter(word != "utterson") %>%
  filter(word != "jekyll") %>%
  filter(word != "van") %>%
  filter(word != "helsing") %>%
  filter(word != "carmilla") %>%
  filter(word != "hyde") %>%
  filter(word != "lucy") %>%
  filter(word != "mina") %>%
  filter(word != "christine") %>%
  filter(word != "raoul") %>%
  filter(word != "erik") %>%
  filter(word != "richard") %>%
  filter(word != "jonathan") %>% 
  filter(word != "arthur") %>% 
  filter(word != "de") %>% 
  filter(word != "karstein") %>% 
  filter(word != "mircalla") %>% 
  filter(word != "millarca") %>% 
  rename(book = title)

## removing de because it is a french part of speech
```
Time is in the top ten for all of them except for in Jekyll and Hyde.


I have also decided to make word clouds depicting the most frequently used words in all of the books. 



no_names %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 72))



```{r}

cloudish_gothic <- no_names

write_rds(cloudish_gothic, "gothiclit/cloudish_gothic.rds")
  

write_rds(messy_gothic, "gothiclit/messy_gothic.rds")

```

```{r}

write_rds(tidy_gothic, "gothiclit/tidy_gothic.rds")


## made dirctory for gothic shiny app and made file to use in said shiny app

```

There is terrible inconsistency between my rmd and the shiny app. Goes from gothic_project to gothiclit to gothicproject.

